---
title: "Lab 07 - Modelling course evaluations"
author: "INSERT NAME HERE"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
evals%>%
  ggplot(aes(x=score))+geom_density()

summary(evals$score)
```

*Add your other details and narratives here.*

2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
evals%>%
  ggplot(aes(x=score,y=bty_avg))+geom_point()

evals%>%
  ggplot(aes(x=score,y=bty_avg))+
  geom_jitter()
```

*Add your narrative and other details here.*

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
```

```{r tidy-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score)
```

*Add your linear model here. Don't worry too much about notation, you can use things like score-hat.*

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit,eval=FALSE}
evals%>%
  ggplot(aes(x=bty_avg,y=score))+
  geom_smooth(method=lm,se=FALSE)+
  geom_jitter()
```

3. Interpret the slope of the linear model in context of the data.

score = 3.88 + 0.067 * bty_avg

for each additional increase in beauty, the score is expected to increase by 0.067
people with a beauty score of 0 are expected to score 3.88

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

*Add your interpretation here*

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)
```

*Add your interpretation here* low adjusted r squared values suggest this is not a good fit of linear regression modelling suggesting high variance of response and explanatory variables 

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

score_bty_aug%>%
ggplot(aes(y=.resid,x=.fitted))+
  geom_jitter()+
  geom_hline(yintercept=0,color="red",size=1)
```

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
evals%>%
  group_by(cls_level)%>%
  count(rank)
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
score_rank_fit<-linear_reg()%>%
  set_engine("lm")%>%
  fit(score~rank,data=evals)

tidy(score_rank_fit)

# tidy model output
```

*Add your narrative here.*

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
score_gender_fit<-linear_reg()%>%
  set_engine("lm")%>%
  fit(score~gender,data=evals)

tidy(score_gender_fit)
```

```{r score_gender_intercept, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

*Add your narrative here. Use in-line code!*

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}

score_bty_gender_fit<-linear_reg()%>%
  set_engine("lm")%>%
  fit(score~bty_avg+gender,data=evals)
tidy(score_bty_gender_fit)

glance(score_bty_gender_fit)

evals%>%
  ggplot(aes(x=bty_avg,y=score,colour=gender))+
  geom_jitter()

#score=3.75+0.074*bty_avg+0.172*gender

```

*Add your narrative here.*

```{r eval = FALSE}

score_bty_gender_fit_aug<-augment(score_bty_gender_fit$fit)

score_bty_gender_fit_aug%>%
  ggplot(aes(x=.resid,y=.fitted,colour=gender))+
  geom_jitter()

```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# 5.5%
```


3. What is the equation of the line corresponding to just male professors?

```{r}
score_bty_gender_fit<-linear_reg()%>%
  set_engine("lm")%>%
  fit(score~bty_avg+gender,data=evals)
tidy(score_bty_gender_fit)
```


4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

adjusted r squared for score_bty_gender is higher meaning it is a better fit of linear regression modelling suggesting lower variance of response and explanatory variables 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)$adj.r.squared
glance(score_bty_gender_fit)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*the slope when adding gender to the equation makes it steeper meaning when all else is held constant an increase in score results in a higher increased in beauty*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
